### 2020-12-07 EPIPHANY2019proceedings_arXiv/Bellini_Epiphany2019_proc.tex
Macros and output for additional figures derived from the Frascati paper

\documentclass{appolb}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{tabularx} 
\usepackage{rotating,graphicx} 
\usepackage{appendix} 
\usepackage{makecell}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage[amssymb]{SIunits}
\usepackage{hyperref}

\usepackage{lineno}
\linenumbers

% graphicx package included for placing figures in the text
%------------------------------------------------------
\input{./commands.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                %
%    BEGINNING OF TEXT                           %
%                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
% \eqsec  % uncomment this line to get equations numbered by (sec.num)
\title{Testing production scenarios for (anti-)(hyper-)nuclei with multiplicity-dependent measurements at the LHC}
\author{F. Bellini\footnote{Presenter.} and A. P. Kalweit 
	\address{European Organisation for Nuclear Research, Geneva \\E-mail: francesca.bellini@cern.ch}}
\thanks{Proceedings of the XXV Cracow EPIPHANY Conference on Advances in Heavy Ion Physics}%

\maketitle
\begin{abstract}
The production of light anti- and hyper-nuclei provides unique observables to characterise the system created in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions. In particular, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, kaons, protons, etc.), because their size is comparable to a fraction or the whole system created in the collision. Their formation is typically described within the framework of coalescence and thermal-statistical production models. 
In order to distinguish between the two production scenarios, we propose to measure the coalescence parameter $B_A$ for different anti- and hyper-nuclei (that differ by mass, size and internal wave-function) as a function of the size of the particle emitting source. 
The latter can be controlled by performing systematic measurements of light anti- hyper- nuclei in different collision systems (pp, pA, AA) and as a function of the multiplicity of particles created in the collision. 
While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light nuclei in heavy-ion collisions, our study shows that large differences can be expected for hyper-nuclei with extended wave-functions, as the hyper-triton. We compare the model predictions with data from the ALICE experiment and we discuss perspectives for future measurements with the upgraded detectors during the High-Luminosity LHC phase in the next decade. 
\end{abstract}

@@

\begin{table}[htb]
\resizebox{\textwidth}{!}{%
\centering
\begin{tabularx}{1.25\textwidth}{cccccccc}
\hline \hline \\[-2ex]
\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs. \\[1ex]  \hline \\[-2ex] 
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]  \hline \hline
\end{tabularx}
}
\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$. $B_{E}$ is the binding energy in MeV.   The size parameter $r_{A}$, is chosen to approximately reproduce the measured/expected rms,  \rmsradius$^{meas}$~(fm). The proton rms charge radius $\lambda_{p} = 0.879(8)$ fm is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents. Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.}
\label{tab:nucleusradii}
\end{table}

\subsection{The coalescence approach}
In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963, Kapusta:1980, Scheibl:1998tk}.
The coalescence probability is encoded in the coalescence parameter, $B_{A}$.
Considering that at LHC energies the number of produced protons and neutrons at midrapidity as well as their momentum distributions are expected to be equal, $B_{A}$ is defined as
%
%
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p,n}}\frac{\mathrm{d}^{3}N_{\mathrm{p,n}}}{\mathrm{d}p_{\mathrm{p,n}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.,
\label{eq:BA}
\end{equation}
%
%
where $p_{\mathrm{p,n}}$ are the proton and neutron momenta and $E_{p,n}$ their energies. 
Equation~\ref{eq:BA} represents also the operative definition of $B_A$ that is used by experiments like ALICE to extract the coalescence probability starting from the measured nucleus and nucleon (proton) distributions.
Starting from the model described in~\cite{Scheibl:1998tk, Blum:2017qnn}, we have obtained in \cite{Bellini:2018epz} a generalised expression for $B_A$
%
%
\begin{equation}\label{eq:master}
B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{\frac{3}{2}(A-1)} \;\;,
\end{equation}
%
%
\noindent which is a function of the spin of the particle $J_A$, its transverse mass $m_{\rm T}$, its size parameter $r_A$ and the source radius $R$. Very importantly, Eq.~\ref{eq:master} takes explicitly into account the source size ($R$), as the coalescence probability naturally decreases for nucleons with similar momenta that are produced far apart in configuration space. 
Moreover, the source size is identified with the  effective sub-volume of the whole system that is governed by the (momentum-dependent) homogeneity length of the interacting nucleons and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry~\cite{Scheibl:1998tk, Blum:2017qnn}. 
Figure~\ref{Fig:BA} shows the source radius dependence of $B_A$ for nuclei and hyper-nuclei with $A = 2, 3$ and 4 whose properties are reported in Tab.~\ref{tab:nucleusradii}. 
For the cases in which more than one estimate for $r_A$ is available, we have adopted the lowest value for the calculations in Fig.~\ref{Fig:BA}.
%
%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.8\textwidth]{coalescenceBA075.eps}
\caption{(Color online) Coalescence parameter $B_A$ as a function of the source radius $R$ as predicted from the coalescence model (Eq.~\ref{eq:master}) for various composite objects with \pt$/A$~=~0.75~\GeVc. For each (hyper-)nucleus, the radius $r$ used for the calculation is reported in the legend.}
\label{Fig:BA}
\end{center}
\end{figure} 
%
%
We observe that the coalescence probability decreases with increasing mass number and $B_A$ decreases with increasing volume. 
For a given $A$, the larger the object radius, the lower is $B_A$, as clearly visible by comparing \hethree~and \hthreelambda. 
For objects with same $A$, mass and spin (e.g. the isobars \tritium~and \hethree), $B_A$ differs only due to the different radius $r_A$. 
This difference is more relevant in small systems, because in large systems the difference between nucleus radii is much smaller than the size of the source.  
Incidentally, this could be experimentally verified with high-precision measurements of the production of \tritium~relative to \hethree~in pp and \pPb~collisions. 
The production of objects with radius larger than the source is strongly suppressed, indicating that the process is driven by the length scale defined by the object radius relative to the source radius.

\subsection{Thermal + blast-wave model} 
Thermal-statistical models~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light \mbox{(anti-)}(hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC. 
In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV. 
Particle yields are derived from the partition function assuming a Grand Canonical ensemble\footnote{Extensions to small systems employ a canonical ensemble partition function to account for the exact conservation of quantum numbers in a finite size system, see for instance~\cite{Vovchenko:2018fiy}.} and they depend only on the mass of the particle and the temperature of chemical freeze-out, d$N$/d$y\propto$~(2$J_A$+1)exp$(-m_{A}/T_{\mathrm{chem}})$.
The thermal model cannot -- alone -- be compared to the \pt-dependent coalescence description because it provides only predictions for \pt-integrated yields. 
A thermal particle production implies a Boltzmann distribution of the momenta only for a static source, which is not the case of the rapidly expanding system produced in heavy-ion collisions. 
The thermal model (i.e. the GSI-Heidelberg implementation we have considered here) needs to be complemented by a hydrodynamic description of the rapidly expanding source. 
To that end, we use the Blast-Wave model~\cite{Schnedermann:1993ws}, which has been proven to describe reasonably well the measured momentum distributions of protons~\cite{Abelev:2013vea}. 
Our ``thermal+blast-wave'' approach results from the combination of the two models: the \pt-dependence is modelled by the blast-wave whereas the normalisation (i.e. the \pt-integrated yield) is taken from the thermal model predictions.
In particular, to describe the (hyper-)nucleus transverse momentum distributions we use the blast-wave parameters obtained from the simultaneous fit to pion, kaon and proton spectra measured in \PbPb~collisions by ALICE for several centralities/multiplicities and reported in~\cite{Abelev:2013vea}. We therefore inherit the multiplicity-dependence of the radial expansion of the system from the measurements. The object size does not enter in the formulation of the blast-wave model. 
In our thermal+blast-wave model, for each centrality/multiplicity class, the coalescence parameter is extracted according to Eq.~\ref{eq:BA} (as done for data) from the predicted (hyper-)nucleus spectrum and the proton spectrum measured by ALICE~\cite{Abelev:2013vea}.

@@

\begin{center}
\includegraphics[width=0.8\textwidth]{B3vsMult073.png}
\caption{(Color online) Coalescence parameter $B_3$ for \hethree~as a function of the average charged particle multiplicity density~\avdNdeta. The coalescence calculation (continuous black line) is compared to two thermal+blast-wave predictions (dashed lines), obtained by using the Grand Canonical (GC, red)~\cite{Andronic:2017} and Canonical Statistical Model (CSM, blue) \cite{Vovchenko:2018fiy} expectations for the \hethree~yield, respectively. ALICE data from pp (green circles) and \PbPb~(red circles) collisions~\cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015} are reported. }
\label{Fig:3He}
\end{center}
\end{figure}

>>>>

\documentclass[a4paper,11pt]{article} 
\usepackage[margin=2.5cm]{geometry}\usepackage{graphicx}
\usepackage{multirow}
\usepackage{tabularx} 
\usepackage{rotating,graphicx} 
\usepackage{appendix} 
\usepackage{makecell}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{cite}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage[amssymb]{SIunits}
\usepackage{hyperref}

\usepackage{lineno}
%\linenumbers

%------------------------------------------------------
\input{./commands.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                %
%    BEGINNING OF TEXT                           %
%                                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}

{\Large \textbf{Testing production scenarios for (anti-)(hyper-)nuclei with multiplicity-dependent measurements at the LHC}}

\medskip

Francesca Bellini\footnote{Presented at the XXV Cracow EPIPHANY Conference on Advances in Heavy Ion Physics}\footnote{Contacts: fbellini@cern.ch, akalweit@cern.ch} and Alexander P. Kalweit
\\European Organization for Nuclear Research (CERN), Geneva, Switzerland

\medskip

\end{center}

\begin{abstract}
The production of light anti- and hyper-nuclei provides unique observables to characterise the system created in high energy proton-proton (pp), proton-nucleus (pA) and nucleus-nucleus (AA) collisions. In particular, nuclei and hyper-nuclei are special objects with respect to non-composite hadrons (such as pions, kaons, protons, etc.), because their size is comparable to a fraction or the whole system created in the collision. Their formation is typically described within the framework of coalescence and thermal-statistical production models. 
In order to distinguish between the two production scenarios, we propose to measure the coalescence parameter $B_A$ for different anti- and hyper-nuclei (that differ by mass, size and internal wave-function) as a function of the size of the particle emitting source. 
The latter can be controlled by performing systematic measurements of light anti- hyper- nuclei in different collision systems (pp, pA, AA) and as a function of the multiplicity of particles created in the collision. 
While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light nuclei in heavy-ion collisions, our study shows that large differences can be expected for hyper-nuclei with extended wave-functions, as the hyper-triton. We compare the model predictions with data from the ALICE experiment and we discuss perspectives for future measurements with the upgraded detectors during the High-Luminosity LHC phase in the next decade. 
\end{abstract}

@@

\begin{table}[htb]
\resizebox{\textwidth}{!}{%
\centering
\begin{tabularx}{1.\textwidth}{cccccccc}
\hline \hline \\[-2ex]
\makecell{Mass \\number } & Nucleus           &  \makecell{Compo-\\sition}               & $B_{E}$ (MeV)   & \makecell{Spin \\$J_{A}$} & \makecell{(Charge) \\rms radius \\ \rmsradius$^{meas}$~(fm)} &  \makecell{Harmonic \\ oscillator \\ size \\ parameter \\$r_{A}$ (fm) } & Refs. \\[1ex]  \hline \\[-2ex] 
      A = 2                     & d                                    & pn                                  &   2.224575 (9)     &     1   & 2.1413 $\pm$ 0.0025      &  3.2    &   \cite{VanDerLeun:1982bhg,Mohr:2015ccw}     \\[0.5ex]  \hline \\[-2ex]
\multirow{3}{*}{A = 3}  & \tritium 	                  & pnn                               &    8.4817986 (20) & 1/2   &  1.755  $\pm$ 0.086        &  2.15   &   \cite{Purcell:2015gtm}           \\
                                   & \hethree                         & ppn                                &   7.7180428  (23) & 1/2  & 1.959 $\pm$  0.030         &   2.48  &   \cite{Purcell:2015gtm} \\
                                   & \hthreelambda               & p$\Lambda$n                &    0.13 $\pm$ 0.05 & 1/2  &  4.9 --  10.0                    &  6.8 -- 14.1 & \cite{Davis:2005mb,Nemura:1999qp} \\[0.5ex]  \hline \\[-2ex]
\multirow{4}{*}{A = 4}  & \hefour                          & ppnn                              &    28.29566   (20)  &      0  &  1.6755 $\pm$ 0.0028  &  1.9  & \cite{1674-1137-41-3-030003,Angeli:2013epw} \\
                                   & \hfourlambda                & p$\Lambda$nn              &  2.04 $\pm$0.04   &   0   &    2.0 -- 3.8             & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp} \\
                                   & \hfourtwolambda          &  p$\Lambda\Lambda$n &   0.39 -- 0.51         &    1     &    4.2 -- 7.1          & 5.5 -- 9.4  &   \cite{Nemura:1999qp} \\
                                   & \hefourlambda              & pp$\Lambda$n              &  2.39 $\pm$ 0.03  &    0   &    2.0 -- 3.8            & 2.4 -- 4.9  & \cite{Davis:2005mb,Nemura:1999qp}\\[0.5ex]  \hline \hline
\end{tabularx}
}
\caption{Properties of nuclei and hyper-nuclei with mass number $A \leq 4$. $B_{E}$ is the binding energy in MeV.   The size parameter $r_{A}$, is chosen to approximately reproduce the measured/expected rms,  \rmsradius$^{meas}$~(fm). The proton rms charge radius $\lambda_{p} = 0.879(8)$ fm is subtracted quadratically from the measured rms charge radius $\rmsradius^{meas}$ of the nucleus $\rmsradius = \sqrt{(\rmsradius^{meas})^2 - {\lambda_{p}^2}}$ to account for the finite extension of the constituents. Implicitly we assume here that $\lambda_{\Lambda}\approx \lambda_{n}\approx \lambda_{p}$.}
\label{tab:nucleusradii}
\end{table}

\subsection{The coalescence approach}
In the coalescence picture, nucleons produced in the collision coalesce into nuclei if they are close in space and have similar velocities \cite{Butler:1963, Kapusta:1980, Scheibl:1998tk}.
The coalescence probability is encoded in the coalescence parameter, $B_{A}$.
Considering that at LHC energies the number of produced protons and neutrons at midrapidity as well as their momentum distributions are expected to be equal, $B_{A}$ is defined as
%
%
\begin{equation}
E_{A}\frac{\mathrm{d}^{3}N_{A}}{\mathrm{d}p_{A}^{3}}=B_{A}{\left(E_{\mathrm{p,n}}\frac{\mathrm{d}^{3}N_{\mathrm{p,n}}}{\mathrm{d}p_{\mathrm{p,n}}^{3}}\right)^{A}}\left\vert_{\vec{p}_{\mathrm{p}}=\vec{p}_{\mathrm{n}}=\frac{\vec{p}_{A}}{A}} \right.,
\label{eq:BA}
\end{equation}
%
%
where $p_{\mathrm{p,n}}$ are the proton and neutron momenta and $E_{p,n}$ their energies. 
Equation~\ref{eq:BA} represents also the operative definition of $B_A$ that is used by experiments like ALICE to extract the coalescence probability starting from the measured nucleus and nucleon (proton) distributions.
Starting from the model described in~\cite{Scheibl:1998tk, Blum:2017qnn}, we have obtained in \cite{Bellini:2018epz} a generalised expression for $B_A$
%
%
\begin{equation}\label{eq:master}
B_{A} = {2J_{A} + 1 \over 2^{A}} {1 \over \sqrt{A}} {1 \over m_{T}^{A-1}} \Bigl({2\pi \over R^2 + ({r_A \over 2})^2 }\Bigr)^{\frac{3}{2}(A-1)} \;\;,
\end{equation}
%
%
\noindent which is a function of the spin of the particle $J_A$, its transverse mass $m_{\mathrm{T}}$, its size parameter $r_A$ and the source radius $R$. Very importantly, Eq.~\ref{eq:master} takes explicitly into account the source size ($R$), as the coalescence probability naturally decreases for nucleons with similar momenta that are produced far apart in configuration space. 
Moreover, the source size is identified with the  effective sub-volume of the whole system that is governed by the (momentum-dependent) homogeneity length of the interacting nucleons and experimentally accessible with Hanbury-Brown-Twiss (HBT) interferometry~\cite{Scheibl:1998tk, Blum:2017qnn}. 
Figure~\ref{Fig:BA} shows the source radius dependence of $B_A$ for nuclei and hyper-nuclei with $A = 2, 3$ and 4 whose properties are reported in Tab.~\ref{tab:nucleusradii}. 
For the cases in which more than one estimate for $r_A$ is available, we have adopted the lowest value for the calculations in Fig.~\ref{Fig:BA}.
%
%
\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.8\textwidth]{coalescenceBA075.eps}
\caption{(Color online) Coalescence parameter $B_A$ as a function of the source radius $R$ as predicted from the coalescence model (Eq.~\ref{eq:master}) for various composite objects with \pt$/A$~=~0.75~\GeVc. For each (hyper-)nucleus, the radius $r$ used for the calculation is reported in the legend.}
\label{Fig:BA}
\end{center}
\end{figure} 
%
%
We observe that the coalescence probability decreases with increasing mass number and $B_A$ decreases with increasing volume. 
For a given $A$, the larger the object radius, the lower is $B_A$, as clearly visible by comparing \hethree~and \hthreelambda. 
For objects with same $A$, mass and spin (e.g. the isobars \tritium~and \hethree), $B_A$ differs only due to the different radius $r_A$. 
This difference is more relevant in small systems, because in large systems the difference between nucleus radii is much smaller than the size of the source.  
Incidentally, this could be experimentally verified with high-precision measurements of the production of \tritium~relative to \hethree~in pp and \pPb~collisions. 
The production of objects with radius larger than the source is strongly suppressed, indicating that the process is driven by the length scale defined by the object radius relative to the source radius.

\subsection{Thermal + blast-wave model} 
Thermal-statistical models~\cite{Andronic:2010qu, Andronic:2017} have been successful in describing the production of light (anti-) (hyper-)nuclei across a wide range of energies in AA collisions, including production at the LHC. 
In this approach, particles are produced from a fireball in thermal equilibrium with temperatures of $T_{chem} \approx$ 156 MeV. 
Particle yields are derived from the partition function assuming a Grand Canonical ensemble\footnote{Extensions to small systems employ a canonical ensemble partition function to account for the exact conservation of quantum numbers in a finite size system, see for instance~\cite{Vovchenko:2018fiy}.} and they depend only on the mass of the particle and the temperature of chemical freeze-out, d$N$/d$y\propto$~(2$J_A$+1)exp$(-m_{A}/T_{\mathrm{chem}})$.
The thermal model cannot -- alone -- be compared to the \pt-dependent coalescence description because it provides only predictions for \pt-integrated yields. 
A thermal particle production implies a Boltzmann distribution of the momenta only for a static source, which is not the case of the rapidly expanding system produced in heavy-ion collisions. 
The thermal model (i.e. the GSI-Heidelberg implementation we have considered here) needs to be complemented by a hydrodynamic description of the rapidly expanding source. 
To that end, we use the Blast-Wave model~\cite{Schnedermann:1993ws}, which has been proven to describe reasonably well the measured momentum distributions of protons~\cite{Abelev:2013vea}. 
Our ``thermal+blast-wave'' approach results from the combination of the two models: the \pt-dependence is modelled by the blast-wave whereas the normalisation (i.e. the \pt-integrated yield) is taken from the thermal model predictions.
In particular, to describe the (hyper-)nucleus transverse momentum distributions we use the blast-wave parameters obtained from the simultaneous fit to pion, kaon and proton spectra measured in \PbPb~collisions by ALICE for several centralities/multiplicities and reported in~\cite{Abelev:2013vea}. We therefore inherit the multiplicity-dependence of the radial expansion of the system from the measurements. The object size does not enter in the formulation of the blast-wave model. 
In our thermal+blast-wave model, for each centrality/multiplicity class, the coalescence parameter is extracted according to Eq.~\ref{eq:BA} (as done for data) from the predicted (hyper-)nucleus spectrum and the proton spectrum measured by ALICE~\cite{Abelev:2013vea}.

@@

\begin{figure}[!htb]
\begin{center}
\includegraphics[width=0.8\textwidth]{B3vsMult073.png}
\caption{(Color online) Coalescence parameter $B_3$ for \hethree~as a function of the average charged particle multiplicity density~\avdNdeta. The coalescence calculation (continuous black line) is compared to two thermal+blast-wave predictions (dashed lines), obtained by using the Grand Canonical (GC, red)~\cite{Andronic:2017} and Canonical Statistical Model (CSM, blue) \cite{Vovchenko:2018fiy} expectations for the \hethree~yield, respectively. ALICE data from pp (green circles) and \PbPb~(red circles) collisions~\cite{ALICE:nucleipp2017,ALICE:deuteronppPbPb2015} are reported. }
\label{Fig:3He}
\end{center}
\end{figure}
